\section{Censorship of IPv4 and IPv6 Resolvers}
\label{sec:infrastructure}

\para{Overview.} In this section, we focus on the difference in censorship
for DNS queries sent to the \textbf{IPv4 and IPv6 interfaes of resolvers}.
%
Specifically, we answer the following questions:
%
(\Cref{sec:infrastructure:country}) In which countries are the DNS censorship
mechanisms for IPv4 and IPv6 traffic significantly different?,
%
(\Cref{sec:infrastructure:resolvers}) what are the characteristics of resolvers
that exhibit differences in the censorship of IPv4 and IPv6 traffic?, and
%
(\Cref{sec:infrastructure:domains}) what are the characteristics of the domains
in which such differences are frequently exhibited?

% \subsection{Within-country differences in the censorship of IPv4 and IPv6 DNS
\subsection{IPv4 vs IPv6 infrastructure censorship} \label{sec:infrastructure:country}

%We use the responses received from the IPv4 and IPv6 interfaces of each of the
%resolvers in our dataset for the same set of domains. We then apply the
%censorship detection mechanism detailed in \Cref{sec:methodology:censorship} to
%measure the prevalence of DNS censorship of queries sent over IPv4 and IPv6.
%Finally, we perform statistical tests to identify the countries that have
%significant differences in their censorship of IPv4 and IPv6 DNS traffic.

%\para{Identifying differences within a country.} 
%
To measure differences in censorship of DNS queries sent over IPv4 and IPv6 we
examine distributions similar to \Cref{sec:resources:country} but this time
investigate two distributions (corresponding to the IPv4 and IPv6 interfaces of
resolvers) of the fraction of censored domains from resolvers within the
corresponding country.
%
We again use a two-sample $t$-test to with \Sidak correction ($p \leq
1-{.05}^{1/n_{c}}$, where $n_c$ is
the total number of countries in our dataset (106)) to verify statistical
significance of any observed differences.
%between the two groups for each country and apply a \Sidak
%correction to control for Type I errors from multiple hypothesis testing. 
%
%
The presence of a statistically significant difference for a specific country
would imply that the country appears to have different censorship mechanisms
for IPv4 and IPv6 DNS traffic (if a centralized mechanism for censorship
exists) or that a significant number of resolvers within that country are not
consistent in their censorship of IPv6 and IPv4 traffic.
%
A summary of our results are presented in \Cref{tab:infrastructure:countries}.

\para{Which countries demonstrate large-scale inconsistencies in their
handling of IPv4 and IPv6 DNS traffic?}
%
In total, we find only five countries (Thailand, Iran, Bangladesh, Myanmar, and
the United States) with statistically significant differences in their handling
of DNS queries over IPv4 and IPv6 traffic --- suggesting the use of independent
censorship mechanisms for IPv4 and IPv6. 
%
Interestingly, all these countries appear to have gaps in their IPv6 censorship
apparatus --- \ie IPv4 rates of blocking are higher than IPv6 rates in all
countries with significant differences. These differences result in IPv6
queries experiencing between 12\% and 78\% less censorship than their IPv4
counterparts.
%
Once again, this suggests a tendency for network operators to more effectively
maintain IPv4 DNS censorship infrastructure than IPv6 infrastructure. These
gaps present opportunities for the success of circumvention tools with IPv6
capabilities.  
%
Further analysis shows that these differences primarily apply to {\tt A}
queries, suggesting that these countries fail to censor most {\tt A} queries
when they are sent over IPv6, but that they are able to censor
{\tt AAAA} records sent over IPv6 effectively.
%
%but not {\tt A} queries sent over IPv6. %This could be due to parsing
%assumptions that a censor's middlebox makes (e.g. that {\tt A} records should
%only appear in IPv4 traffic). These findings are particularly noteworty for
%circumvention efforts in Thailand, Myanmar, and Iran where IPv6 adoptoin rates
%are high~\cite{Google-IPv6}.
%Further analysis shows that these differences primarily arise due to the fact
%that DNS type {\tt A} queries are significantly more likely to be blocked over
%IPv4 connections than over an IPv6 connection. However, this is not the case
%for {\tt AAAA} queries, with the exception of Iran.
%
%aken together, 
These findings are particularly noteworthy for circumvention
efforts in Thailand, Myanmar, and Iran where IPv6 adoption rates are high
(between 15\% and 45\%) and dual-stack tools may be used for circumvention of
DNS censorship.
%

\begin{table}[t]
  \centering
  \small
  \scalebox{\tabularscale} {
  \begin{tabular}{lccc}%p{.9in}p{.9in}}
    \toprule
    {\bf Country}&{\bf {\tt A} queries }&{\bf {\tt AAAA} queries} & {\bf All queries}
    \\ \midrule
    Thailand (TH)      & -7.1 pp (-86.3\%) & $ns$              & -3.7 pp (-78.1\%) \\
    Iran (IR)          & -3.2 pp (-12.6\%) & -3.0 pp (-12.5\%) & -3.1 pp (-12.5\%) \\ 
    Bangladesh (BD)    & -5.5 pp (-86.1\%) & $ns$              & -3.0 pp (-77.9\%) \\
    Myanmar (MY)       & -3.6 pp (-74.2\%) & $ns$              & -2.1 pp (-62.3\%) \\
    United States (US) & -0.9 pp (-64.8\%) & $ns$              & -0.5 pp (-42.6\%) \\
    \midrule
    Korea (KR)         & -1.1pp (-46.5\%) & $ns$    & $ns$ \\
    Chile (CL)         & -1.6pp (-58.7\%)  & $ns$    & $ns$ \\
    \bottomrule
  \end{tabular}
  }
  \caption{Differences in blocking rates of DNS queries sent to IPv4 and IPv6
  interfaces of each resolver in a country. `pp' denotes the change in
  terms of percentage points (computed as blocking rate of IPv6 - blocking
  rate of IPv4) and the \%age value denotes the percentage change in blocking rate
  (computed as 
  $
  100 \times \frac{\text{IPv6 blocking rate} - \text{IPv4 blocking rate}}
  {\text{IPv4 blocking rate}}
  $). 
  Only countries having a statistically significant difference are reported. A
  negative value indicates that queries sent over IPv4 observed higher blocking
  rates than those sent over IPv6 in a given country. $ns$ indicates the
  difference was not statistically significant and thus omitted. Korea and Chile
  are included separately as they demonstrated significant difference in
  \texttt{A}/\texttt{AAAA} censorship (\Cref{sec:resources:country}).}
  \label{tab:infrastructure:countries}
\end{table}

% \subsection{Characteristics of IPv4/IPv6-inconsistent resolvers}
\subsection{IPv4/IPv6-inconsistent resolvers}
\label{sec:infrastructure:resolvers}
%

Next, we look at the characteristics of resolver pairs that see inconsistent
censorship on their IPv4 and IPv6 interfaces. 

%Our previous results demonstrate the promise of using IPv6 channels for DNS
%resolution to bypass IPv4 DNS censorship. We now focus on identifying the
%distribution and connection-type of resolvers demonstrating inconsistencies in
%their handling of IPv4 and IPv6 traffic. This serves two purposes:
%%
%First, our analysis on the distribution of IPv4/IPv6-inconsistent resolvers
%provides evidence-driven hypotheses about how information control deployments
%are structured in different countries. 
%%
%Second, studying the connection-types of IPv4/IPv6-inconsistent resolvers sheds
%light on whether the gaps in censorship are visible to users in residential
%networks. This serves as an indicator for the potential gains to be had by
%circumvention tools that begin exploiting the IPv4/IPv6 gap.
%
\para{Identifying IPv4/IPv6-inconsistent resolvers.} Our approach is similar to
the methods used to identify {\tt A/AAAA}-inconsistent resolvers
(\cf \Cref{sec:resources:resolvers}). 
%
We compare the ratios of censored responses received from a single resolver
pair's IPv4 and IPv6 interfaces. We test whether these ratios are statistically
different using a $z$-test with a \Sidak corrected $p \leq 1-.05^{1/n_{r_c}}$
being required for a statistically significant difference. 
%
A summary of the characteristics of the inconsistent resolvers identified in
each country is illustrated in \Cref{tab:infrastructure:resolvers}.

\para{Which countries have the largest fraction of IPv4/IPv6-inconsistent
resolvers?}
%
Two countries from our previous analysis on {\tt A/AAAA}-inconsistencies once
again appear with a large fraction of IPv4/IPv6-inconsistent resolvers ---
Thailand (81\%) and Bangladesh (65\%). Myanmar presents a new addition with
60\% of its resolvers demonstrating IPv4/IPv6-inconsistencies. Other countries
were found to have smaller fractions ranging from 12-26\%.

\para{How spread out are the IPv4/IPv6-inconsistent resolvers?}
%
In order to characterize the spread of IPv4/IPv6-inconsistent resolvers within
a country, we compute the entropy of the AS distribution of all resolvers and
IPv4/IPv6-inconsistent resolvers within a country
($S^{\text{all}}_{\text{net}}$ and $S^{\text{inconsistent}}_{\text{net}}$) and
then compute the KL-divergence of the distribution of inconsistent resolvers
from the distribution of all resolvers in that country ($\nabla_{net}$).
%
Similar to before, a large change in $\nabla_{net}$ means that the
IPv4/IPv6-inconsistencies arise from a small fraction of ASes and would suggest
that the gaps exist due to local network/resolver configurations --- as
would be the case if regional operators implement their own DNS censorship
mechanisms. Conversely, a small change means that the gaps that exist roughly
equally impact all the ASes having resolvers and would suggest that the gaps
exist due to misconfigurations in a centralized DNS censorship mechanism.
%
Our results again suggest the presence of a centralized blocking mechanism
in Thailand, Bangladesh, and Myanmar ($\nabla_{net} \in [0.13, 0.48]$) which
causes the IPv4/IPv6-inconsistencies. The United States has the highest
$\nabla_{net}$ observed which indicates that regional policies are responsible
for the IPv4/IPv6-inconsistencies. 

\para{What types of networks exhibit the most IPv4 and IPv6 inconsistencies?}
%
An overwhelming majority of the inconsistent resolvers in Thailand, Iran, and
Bangladesh (77\%-100\%) are found to be present in networks with (Maxmind
categorized) Cable/DSL connection-types that are typically associated with
residential networks. 
%
Put in the context of our previous result which suggests the presence of
a centralized DNS censorship mechanism in Thailand and Bangladesh, this
suggests that the IPv4/IPv6 gaps that exist in this mechanism also extend to
residential networks in the country.
%
Myanmar and the United States experience such inconsistencies primarily due to
their corporate networks which contain between 67-87\% of their inconsistent
resolvers. 

\begin{table*}[t]
  \centering
  \small
  \scalebox{\tabularscale} {
    \begin{tabular}{lcclcccl}
    \toprule
      {\bf Country} & {\bf Total pairs} & {\bf Inconsistent pairs} & {\bf Most inconsistent AS} & \multicolumn{3}{c}{\bf AS diversity} & {\bf Most inconsistent type} \\
      & & {(\% of total pairs)}& {(\# inconsistent pairs)}
      & $S^{\text{all}}_{\text{net}}$ & $S^{\text{inconsistent}}_{\text{net}}$
      & $\nabla_{\text{net}}$  & {(\# inconsistent pairs)} \\
      \midrule
      Thailand (TH)            & 186    & 151 (81.2\%)  & AS 9835 Government IT Services (39)  & 4.50 & 4.10 & 0.13 & Cable/DSL (108) \\
      Iran (IR)                & 277    & 74 (26.7\%)   & AS 208161 PARSVDS (11)               & 5.03 & 3.81 & 0.87 & Cable/DSL (57) \\
      Bangladesh (BD)          & 29     & 19 (65.2\%)   & AS 9230 Bangladesh Online (4)        & 4.10 & 3.72 & 0.39 & Cable/DSL (19) \\
      Myanmar (MY)             & 50     & 30 (60.0\%)   & AS 136170 Exabytes Network (10)      & 3.31 & 2.42 & 0.48 & Corporate (26) \\
      United States (US)       & 1,228  & 151 (12.3\%)  & AS 30457 WEHOSTWEBSITES (36)         & 6.28 & 5.22 & 1.44 & Corporate (102) \\
      \midrule                 
      Korea (KR)               & 632    & 101 (16.0\%)  & AS 9848 Sejong Telecom (13)          & 3.12 & 4.14 & 0.95 & Cable/DSL (73)   \\
      Chile (CL)               & 65     & 16 (24.6\%)   & AS 27651 Entel Chile (12)            & 3.08 & 1.19 & 1.04 & Corporate (11) \\
    \bottomrule
  \end{tabular}
  }
  \caption{Characteristics of the resolvers which demonstrated a statistically
  significant difference in their handling of DNS queries over IPv4 and IPv6
  each country.
  %
  `AS diversity' denotes the entropies of (all) resolver distribution
  ($S^{\text{all}}_{\text{net}}$) and {IPv4/IPv6}-inconsistent resolver
  distribution ($S^{\text{inconsistent}}_{\text{net}}$) across a country's
  ASes, and `$\nabla_{\text{net}}$' represents the Kullback-Leibler divergence
  of the distribution of inconsistent resolvers from the distribution of all
  resolvers in the country's ASes (\cf \Cref{sec:infrastructure:resolvers}).
  %
  `Most inconsistent type' denotes the connection type with the most number of
  {IPv4/IPv6}-inconsistent resolvers.Korea and Chile are included separately as
  they demonstrated significant difference in \texttt{A}/\texttt{AAAA}
  censorship (\Cref{sec:resources:country}).}
  \label{tab:infrastructure:resolvers}
\end{table*}

\subsection{Characterization of anomalous domains}
\label{sec:infrastructure:domains}
We now seek to understand the category of domains that get through the
infrastructural gap between DNS queries over IPv4 and IPv6. In other words,
does the category of domain influence whether or not there is a difference in
censorship between IPv4 and IPv6 interfaces?
%We provide a general
%categorization of these domains and further compare this category distribution
%with that of domains that received any blocking. We do this in order to identify
%specific mechanisms that might differ for censorship of certain categories over
%IPv4 and IPv6.

\para{Identifying differences in domain behaviors within a country}
We use an approach similar to the one defined in \Cref{sec:resources:domains}
for identifying domains that get through the gap in between IPv4 and IPv6. For
each domain, we measure the ratio of blocking that occurs over IPv4 and IPv6. We
then apply the $z$-test with a corrected $p$-value (as described in
\Cref{sec:resources:domains}) to these ratios. This gives us all domains which
had significant differences in censorship over IPv4 and IPv6.

\para{Do these IPv4/IPv6-inconsistent domains hint at policy gaps?}
For each country, we derive domain categories for the following two lists; (1)
$\text{D}_{\text{any}}$ which contains the domains which experienced any
blocking events inside a country and (2) $\text{D}_{\text{inconsistent}}$ which
contains the IPv4- and IPv6-inconsistent domains identified by our $z$-test. We
again used KL-divergence between to compare these two category distributions. A
small $\nabla_{\text{net}}^{\text{domains}}$ would signify that the two
category distributions are not largely different suggesting the policy gap over
IPv4/IPv6 is not content specific; A large
$\nabla_{\text{net}}^{\text{domains}}$ would signify that the category
distributions are indeed very different suggesting a content-based policy gap.
\\
Based on this analysis, we see that Bangladesh, US and Iran have the smallest
$\nabla_{\text{net}}^{\text{domains}}$ scores (0-1.3) suggesting that there
was little to no difference in the distribution of the two categories. This
suggests that for these countries, there is no content-based policy gaps. On the
other hand, Pakistan, China and Myanmar had the highest
$\nabla_{\text{net}}^{\text{domains}}$ scores (2.7-4.3). These scores suggest
that some categories of domains get through the IPv4/IPv6 censorship gap much
more than others. "Gambling" is the category most likely to get through this gap
for China and Pakistan and "Government/Military" is the most likely to get
through this gap in Iran. 
